---
title: "Restaurant Ratings Analysis"
author: "MD Salek Miah, Statistics(2/2) at SUST"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: custom_styles.docx
  pdf_document: default
---

## Introduction

This report analyzes restaurant ratings based on various factors such as cuisine type, price, distance, and service model. It identifies the best and worst restaurant configurations based on the average ratings from Talal, Ahmeed, and Omar.

## Data Import and Processing

```{r}
library(readxl)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)

# Define file path
file_path <- "D:\\Shihab vai work\\Dataset\\user_data.xlsx"

# Read data from the "Ratings" sheet
df <- read_excel(file_path, sheet = "Ratings")

# Select relevant columns
df_selected <- df %>% select(Cuisine, Price, Distance, Service, Talal, Ahmeed, Omar)

# Compute the average rating
df_selected <- df_selected %>% mutate(Avg_Rating = rowMeans(select(., Talal, Ahmeed, Omar), na.rm = TRUE))
```

## Best and Worst Restaurant Configurations

```{r}
# Best-rated restaurant configuration
best_config <- df_selected %>% filter(Avg_Rating == max(Avg_Rating))

# Worst-rated restaurant configuration
worst_config <- df_selected %>% filter(Avg_Rating == min(Avg_Rating))

```

## Best Configuration

```{r}
best_config %>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))

```

## Worst Configuration

```{r}
worst_config %>% 
  kable() %>% 
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))

```


# Save the plot
ggsave("histogram_plot.png", width = 6, height = 4, units = "in")

```

## Conclusion

This analysis determines the most and least favored restaurant arrangements based on customer ratings submitted by Talal, Ahmeed, and Omar. Through comparison of their personal ratings:

Talal's ratings indicate favoring [specific aspects he appreciates, e.g., "lower prices and faster service"]. Ahmeed's ratings tend to perform better on [specific areas he prefers, e.g., "cuisines with different menus and better service quality"]. Omar's ratings highlight [mention any unique factors based on his ratings, e.g., "value for money and authenticity in food"].
